Treatment Outcome Visualization

### 2023-05-05 Depression_Vis.Rmd
Adding Website to repo

### plot means based upon duration group membership

@@

## GENDER IDENTITY
Create a New Data Set with an Average Depression Variable and Gender, then plot it
```{r}
#GENDER IDENTITY
#Create a New Data Set with an Average Depression Variable and Gender
Mothership_Mean_CUDOS_Gender<-Mothership_Long_dep %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

>>>>

### Plot means based upon duration of treatment

@@

## GENDER IDENTITY
Create a New Data Set with an Average Depression Variable and Gender, then plot it
```{r}
#Create a New Data Set with an Average Depression Variable and Gender
Mothership_Mean_CUDOS_Gender<-Mothership_Long_dep %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

### 2023-05-05 Diagnosis_Vis.Rmd
Adding Website to repo

---
title: "Diagnosis_Vis"
output: html_document
date: "2023-04-04"
---

@@

## Create Diagnosis Variables 

@@

#### Amount of disorders treated
```{r}
#overall psychiatric disorders
ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
  coord_flip()
```

#### Number of disorders over time.
```{r}
# Libraries
library(ggplot2)
#install.packages("hrbrthemes")
library(hrbrthemes)
library(dplyr)
library(tidyr)
library(viridis)

@@

```

@@

>>>>

---
title: "Diagnosis Visualizations"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

@@

The following code creates visualizations for diagnostic related information. The main difficulty of these visualizations was getting diagnostic variables correctly coded so there was not overlap or double acounting for conditions.

# Create Diagnosis Variables 

@@

# Number of Disorders Treated Over Time

## {.tabset}

### All Disorders
```{r}
# Libraries
library(ggplot2)
#install.packages("hrbrthemes")
library(hrbrthemes)
library(dplyr)
library(tidyr)
library(viridis)

@@

```
### Excluding Mood Disorders

@@

# Amount of Disorder Type Treated 
Grouped into DSM chapter subtypes (e.g., Mood Disorder = Major Depressive Disorder, Bipolar 1 & 2, etc.)

### Amount of Primary Diagnoses
```{r}
# Disorder Type 
ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none")+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
  coord_flip()
```

As you can see, the main disorder type in the hospital is mood realted disorders. This shouldn't be supprising as many indiviudals with suicidality (A common hospitalization issue) will meet criteria for a mood disorder.

### Excluding Mood Disorders
```{r}
# Disorder Type (Without Depression)
ggplot(data = subset(No_depressy, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none")+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
  coord_flip()
```

### Number of Co-occuring Disorders
The following visualization looks at the number of disorders people had, but wasn't the main reason they attended the hospital, or their "main" diagnosis.
```{r}
Mothership_Current_Long <- Mothership %>%
  pivot_longer(
    cols=c(Anxiety_C, Mood_C, Substance_C, Trauma_C, Psychotic_C, Eating_C,  Somatic_C, OCD_Co_C, BPD_Co_C),
    names_to = 'Disorder_Present') %>%
  filter(value != 0) %>%
  select(!value)  %>%
  filter(!is.na(Disorder_Present))%>%
  filter(!is.na(Disorder_Type))

ggplot(data = subset(Mothership_Current_Long, !is.na(Disorder_Present)),mapping = aes(x = Disorder_Present, fill=Disorder_Present))+
  geom_bar()+
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none") +
  labs(title = "Number of Co Occuring Psychiatric Diosrders",
    subtitle = "In Addition to the Primary Diagnosis",
    x = "Co-Occuring Psychiatric Disorder") +
    scale_x_discrete(labels=c("Trauma_C" = "Trauma", 
                            "Substance_C" = "Substance Use",
                            "Somatic_C" = "Somatic",
                            "Psychotic_C" = "Psychotic",
                            "OCD_Co_C" = "OCD",
                            "Mood_C" = "Mood",
                            "Eating_C" = "Eating",
                            "BPD_Co_C" = "BPD",
                            "Anxiety_C" = "Anxiety")) +
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
  coord_flip()
```

# Primary and Co-occuring Disorders.

The following visualization shows which disorders are co-occurring with which types of primary diagnoses. 
```{r}
library(dplyr)
library(tidyr)

Mothership_Current_Long %>%
  ggplot(aes(x = Disorder_Type, y = Disorder_Present, color = Disorder_Type)) +
  geom_count(alpha = .5)+
  scale_size_area(max_size = 20) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Trauma_C" = "Co Trauma", 
                            "Substance_C" = "Co Substance Use",
                            "Somatic_C" = "Co Somatic",
                            "Psychotic_C" = "Co Psychotic",
                            "OCD_Co_C" = "Co OCD",
                            "Mood_C" = "Co Mood",
                            "Eating_C" = "Co Eating",
                            "BPD_Co_C" = "Co BPD",
                            "Anxiety_C" = "Co Anxiety")) +
  labs(title = "Number of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis") 
```

### 2023-05-05 Treatment_Outcomes.Rmd
Adding Website to repo

---
title: "Treatment_Outcomes"
output: html_document
date: "2023-04-14"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

@@

## RDQ stuff
```{r}

#Read in a New Data Set
Mothership_RDQ<- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
Mothership_RDQ<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
Mothership_RDQ<-data.frame(sapply(Mothership_RDQ,FUN=as.numeric))

@@

view(Mothership_Long_RDQ)

@@

```{r, include=FALSE}
# # Depression symptoms df
# CUDOS_Score <- select(Mothership,
#                       Days_complete_1,Day1_CUDOS:Day40_CUDOS)
# 
# # Anxiety symptoms df
# CUXOS_Score <- select(Mothership,
#                       Days_complete_1,Day1_CUXOS:Day40_CUXOS)

@@

```{r, include=FALSE}
#1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
# Mothership <- Mothership %>%
#   mutate(Mothership_Pre_Post, 
#             Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)
#          )
# 
# Mothership$Days_complete_W
# 
# #2. Then create df with CUDOS and CUXOS scores
#   # Depression 
#   
#     CUDOS_Score <- select(Mothership,
#                       Day1_CUDOS:Day40_CUDOS)
# 
#   # Anxiety
#     CUXOS_Score <- select(Mothership,
#                       Day1_CUXOS:Day40_CUXOS)
#     
# #### Figure out how to:
#     #1. write a for /while loop to get a final value. 
#     #2. get values for NAs for days attended, 
#     #3. get values so this can go into the whole mothership dataset. 
#     
#     
#     
#     
# #3. Extract the valeues for each patient at their last day (length of stay)
#  Mothership <- mutate(Mothership,
#             # CUDOS_post = CUDOS_post)
#             CUXOS_post = CUXOS_post)
#     ##### Why is it not includeing NAs.
# 
# CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
# CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
# 
# CUDOS_post
# Mothership %>%
#   mutate(Dep_post = CUDOS_post)
# 
# CUDOS_post
# #4. Extract the value for their first day 
# CUDOS_pre<-Mothership$Day1_CUDOS
# CUXOS_pre<-Mothership$Day1_CUXOS
# AnxDep_PrePost_test <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
# AnxDep_PrePost_test
# colnames(AnxDep_PrePost)[1] = "ID1"
# 
# AnxDep_PrePost_test
# ## This is where I am Figure out where to go from here *******************
# #5. Create long dataframe
# 
# AnxDep_PrePost_Lon <- gather(AnxDep_PrePost,ID1:CUXOS_post,factor_key = "T")
# 
# AnxDep_PrePost_Long <- pivot_longer(AnxDep_PrePost,ID1:CUXOS_post)
# 
# 
# AnxDep_PrePost_Long
# ?pivot_longer()
# 
# AnxDep_PrePost_Long <- AnxDep_PrePost_Long[order(AnxDep_PrePost_Long$ID1),]
# 
# Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
#                               factor_key = "T")
# Mothership_Long_RDQ

@@

>>>>

---
title: "Treatment Outcome Visualization"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

@@

# Remission from Depression Questionnaire (RDQ)

The following code visualizes the outcomes from the RDQ. The RDQ is broken up into the following categories:

1. Coping Skills: (higher score = more coping skills)
2. Positive Mental Health: (higher score = more positive mental health)
3. Functioning: (higher score = better functioning)
4. Well Being: (higher score = better overall well being)
5. Symptoms: (higher score = more severe depression symptoms)

```{r}
#Read in a New Data Set
Mothership_RDQ<- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
Mothership_RDQ<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
Mothership_RDQ<-data.frame(sapply(Mothership_RDQ,FUN=as.numeric))

@@

@@

```{r, include=FALSE}
# Depression symptoms df
# CUDOS_Score <- select(Mothership,
#                       Days_complete_1,Day1_CUDOS:Day40_CUDOS)
# 
# # Anxiety symptoms df
# CUXOS_Score <- select(Mothership,
#                       Days_complete_1,Day1_CUXOS:Day40_CUXOS)

@@

```{r, include=FALSE}
#1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
# 
# 
# Mothership_post <- Mothership %>%
#   mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1))
# 
# 
# 
# Mothership <- Mothership %>%
#   mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1))
#          
# 
# Mothership$Day1_CUDOS
# Mothership$Days_complete_1
# Mothership$Days_complete_W
# 
# view(Mothership)
# #2. Then create df with CUDOS and CUXOS scores
#   # Depression
# 
#     CUDOS_Score <- select(Mothership,
#                       Day1_CUDOS:Day40_CUDOS)
# 
#   # Anxiety
#     CUXOS_Score <- select(Mothership,
#                       Day1_CUXOS:Day40_CUXOS)
# 
# 
# #3. Extract the valeues for each patient at their last day (length of stay)
#     ##### Why is it not includeing NAs.
#     
# 
# CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
# CUXOS_post = CUXOS_Score[cbind(1:length(Mothership$Days_complete_W),Mothership$Days_complete_W)]
# 
# seq_along(Mothership$Days_complete_W)
# Mothership$Days_complete_W
# CUDOS_post
# 
# Mothership %>%
#   mutate(Dep_post = CUDOS_post)
# 
# 
# Mothership %>%
#   mutate(Dep_post = CUDOS_post)
# 
# CUDOS_post
# #4. Extract the value for their first day
# CUDOS_pre<-Mothership$Day1_CUDOS
# CUXOS_pre<-Mothership$Day1_CUXOS
# AnxDep_PrePost_test <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
# AnxDep_PrePost_test
# colnames(AnxDep_PrePost)[1] = "ID1"
# 
# AnxDep_PrePost_test
# ## This is where I am Figure out where to go from here *******************
# #5. Create long dataframe
# 
# AnxDep_PrePost_Lon <- gather(AnxDep_PrePost,ID1:CUXOS_post,factor_key = "T")
# 
# AnxDep_PrePost_Long <- pivot_longer(AnxDep_PrePost,ID1:CUXOS_post)
# 
# 
# AnxDep_PrePost_Long
# ?pivot_longer()
# 
# AnxDep_PrePost_Long <- AnxDep_PrePost_Long[order(AnxDep_PrePost_Long$ID1),]
# 
# Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
#                               factor_key = "T")
# Mothership_Long_RDQ

@@

```{r, include=FALSE}
# Mothership_Post <- Mothership %>%
#   filter(!is.na(Days_complete_1)) %>%
#   mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)) 
#   
# 
# Mothership_Post$Days_complete_W
# 1:length(Mothership_Post$Days_complete_W)
# 
# # Depression
# CUDOS_Score <- select(Mothership_Post, Day1_CUDOS:Day40_CUDOS)
# 
# CUDOS_Score
# 
# 1:length(Mothership_Post$Days_complete_W)
# 
# # Anxiety
# CUXOS_Score <- select(Mothership_Post, Day1_CUXOS:Day40_CUXOS)
# 
# values <- cbind(seq_along(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W[1:8610])
# values
# CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership_Post$Days_complete_W)[1:8610],Mothership_Post$Days_complete_W[1:8610])]
# CUDOS_post
# 
# 
# CUDOS_post = CUDOS_Score[cbind(1:length(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W)]
# CUXOS_post = CUXOS_Score[cbind(1:length(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W)]
# 
# CUDOS_post
# 
# values <- cbind(1:length(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W)
# values
# Mothership_Post<- Mothership_Post %>%
#   mutate(Dep_post = CUDOS_post)
```
